Openness and Computational Reproducibility in plant pathology: where do we stand and a way forward

### 2022-05-16 analysis/paper/paper.Rmd
Wordsmith and fix citations

> "The replication of scientific findings using independent investigators, methods, data, equipment, and protocols has long been, and will continue to be, the standard by which scientific claims are evaluated. However, in many fields of study there are examples of scientific investigations that cannot be fully replicated because of a lack of time or resources. In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing. One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
> Peng, R.
> [-@Peng2009].
> *Reproducible research and Biostatistics*.
> Biostatistics, 10 (3): 405-408.

@@

It goes without saying that plant pathologists already provide information on protocols and chemicals allowing for reproducibility.
However, frequently biological specimens such as strains, cultures or cultivars are not available.
These cases do constitute a lack of reproducibility but will not be covered here.

>>>>

> "The replication of scientific findings using independent investigators, methods, data, equipment, and protocols has long been, and will continue to be, the standard by which scientific claims are evaluated. However, in many fields of study there are examples of scientific investigations that cannot be fully replicated because of a lack of time or resources. In such a situation, there is a need for a minimum standard that can fill the void between full replication and nothing. One candidate for this minimum standard is 'reproducible research', which requires that data sets and computer code be made available to others for verifying published results and conducting alternative analyses".
> @Peng2009.
> *Reproducible research and Biostatistics*.
> Biostatistics, 10 (3): 405-408.

@@

Plant pathologists routinely provide information on protocols and chemicals allowing for reproducibility.
However, frequently biological specimens such as strains, cultures or cultivars are not available after publication.
These cases do constitute a lack of reproducibility but will not be covered here.
